---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    message = FALSE,
    warning = FALSE,
    echo = TRUE,
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures",
    out.width = "100%"
)
options(width = 100)
```

# iNZightTS: Time Series Visualisation and Forecasting

[![R-CMD-check](https://github.com/iNZightVIT/iNZightTS/workflows/R-CMD-check/badge.svg)](https://github.com/iNZightVIT/iNZightTS/actions?workflow=R-CMD-check)
[![Codecov test coverage](https://codecov.io/gh/iNZightVIT/iNZightTS/branch/master/graph/badge.svg)](https://codecov.io/gh/iNZightVIT/iNZightTS?branch=master)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)
[![CRAN](https://www.r-pkg.org/badges/version/iNZightTS)](https://CRAN.R-project.org/package=iNZightTS)

## Overview

The iNZightTS package provides some simple analysis tools for exploring time series data, which is used by [iNZight](https://github.com/iNZightVIT/iNZight). The package uses [tidyverts](https://tidyverts.org/) to store and process time series data and [ggplot2](https://github.com/tidyverse/ggplot2) to produce customisable graphics.

## Installation

The *stable* version can be installed from [CRAN](https://cran.r-project.org/web/packages/iNZightTS/index.html):

```{r cran, eval = FALSE}
install.packages("iNZightTS")
```

Or install the *development* version from [GitHub](https://github.com/iNZightVIT/iNZightTS):

```{r github, eval = FALSE}
remotes::install_github("iNZightVIT/iNZightTS")
```

## Usage

```{r pkgs}
library(iNZightTS)
library(dplyr)
library(tidyr)
```

### Getting started

Use the `inzightts` function to create a temporal data set to be used by the functions of the package. The data is stored as a [tsibble](https://github.com/tidyverts/tsibble).

```{r data}
data <- visitorsQ %>%
    pivot_longer(!Date, names_to = "Country", values_to = "Visitors") %>%
    inzightts(key = "Country")
data
```

### Graphics

Exploratory analysis of time series data starts from a smoothed line plot.

```{r raw-plot}
plot(data)
```

### Decompositions

Time series data often exhibit features such as trend, season and cycle. A decomposition plot breaks the data into visual components which simplies the analysis.

```{r decomp}
dcmp <- data %>%
    filter(Country == "Australia") %>%
    inzightts() %>%
    decomp()
dcmp
```

```{r decomp-plot}
plot(dcmp, title = "Visitors to Australia")
```

### Visualising seasonal effects

Plots are helpful in revealing the underlying seasonal pattern of time series data.

```{r season-plot}
seasonplot(data)
```

```{r subseries-plot}
subseries(data)
```

### Forecasting

```{r forecast}
pred <- predict(data)
summary(pred)
```

```{r forecast-plot}
plot(pred)
```
